---
title: "Assignment 1"
author: "Balint Parragi"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,include=FALSE}
library(tidyverse)
library(fixest)
library(data.table)
library(dplyr)
library(ggplot2)
library(usdata)
```

```{css, echo=FALSE}
h1, h2, h3 , h4 {
  text-align: center;
  font-weight: bold;
}
```

# __Predicting hourly wages of cooks__

- Target variable is `earn_hour`: hourly wage
- Predictors can be:
  + Quantitative: `age`, number of `own children`
  + Categorical: `sex`, `race` and `ethnicity`, `state` of residence, highest `grade` completed, `marital status`, `presence of children`, `citizenship`, `industry classificaton`, `employment class`, `union membership`, and `employment status`
- Some variables can be redundant (i.e the month of the interview), and some categorical variables have many categories that increases the complexity of the models rapidly (i.e `state` of residence with `r length(levels(cps_cooks$state_long))` unique values)




```{r, include=FALSE}
cps <- read.csv("https://osf.io/4ay9x/download", stringsAsFactors = TRUE) %>% data.table()

cps_cooks <- cps %>% 
  filter(occ2012=="4020") %>% 
  mutate(state_long = as.factor(abbr2state(stfips)),
         earn_hour = earnwke/uhours,
         grade92 = as.factor(grade92),
         race = as.factor(race),
         ethnic = as.factor(ethnic),
         sex = as.factor(sex),
         marital = as.factor(marital),
         chldpres = as.factor(chldpres)
         ) %>% 
  select(-c(weight,hhid))

#Note to self about variables (not included in the report):

#X:unique ID; hhid: household id
#intmonth: interview calendar month
#sex: male 1
#chldpres: presence of own children (categorical)
#grade92: highest grade completed
#prcitshp: citizenship
#class: employment class
#earnwke: edited or computed earnings per week
#uhours: how many hours ... usually work per week
#ind02: industry classification code
#unionmme: member of union?
#lfsr94: employment status (working, searching, etc.)
```


```{r}
# Models - OLS regressions
feols(earn_hour ~ age + sex, data = cps_cooks)
feols(earn_hour ~ age + sex + state_long + lfsr94 , data = cps_cooks,vcov = 'hetero')

feols(earn_hour ~ intmonth,data=cps_cooks)
```

```{r}
# Evaluation, comparison
output <- data.frame(
  model   = c(),
  `N vars`   = c(),
  `N coeff` = c(),
  `RMSE full` = c(),
  `RMSE cv` = c(),
  `BIC full` = c(),
)

```

