---
title: "Assignment 2"
author: "Balint Parragi, `r Sys.Date()`"
geometry: left=1cm,right=1cm,top=1.5cm,bottom=1.5cm
fontsize: 8pt
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)
```

```{r,include=FALSE}
library(tidyverse)
library(fixest)
library(data.table)
library(dplyr)
library(ggplot2)
library(caret)
library(kableExtra)
library(gridExtra)
library(grid)
```

```{css, echo=FALSE}
h1, h2, h3 , h4 {
  text-align: center;
  font-weight: bold;
}
```

```{r, include=FALSE}
listings <- fread("data/listings.csv",encoding = "UTF-8")
#midsize apartments, 2-6 guests

listings_clean <- listings %>% 
  select(-c(id,listing_url,scrape_id,last_scraped,source,picture_url,host_url,host_thumbnail_url,host_picture_url,host_neighbourhood,neighbourhood_group_cleansed,calendar_updated,license)) %>% 
  filter(room_type == "Entire home/apt",
         accommodates >= 2 & accommodates <= 6) %>% 
  mutate(price_usd = gsub(",","",price),
         price_usd = as.numeric(gsub("\\$","",price_usd)),
         bathrooms = str_extract(bathrooms_text,"([0-9]*[.])?[0-9]+"),
         bathrooms = ifelse(str_detect(tolower(bathrooms_text),"half"),"0.5",ifelse(bathrooms_text=="","0",bathrooms)),
         bathrooms = as.numeric(bathrooms),
         neighbourhood_cleansed = gsub("\u009f","ü",neighbourhood_cleansed),
         neighbourhood_cleansed = gsub("§","ß",neighbourhood_cleansed),
         neighbourhood_cleansed = gsub("\u009a","ö",neighbourhood_cleansed),
         neighbourhood_cleansed = gsub("\u008a","ä",neighbourhood_cleansed),
         f_neighbourhood_cleansed = factor(neighbourhood_cleansed),
         f_property_type = factor(property_type),
         host_response_rate = as.numeric(ifelse(host_response_rate %in% c("N/A",""),NA,gsub("%","",host_response_rate)))/100,
         host_acceptance_rate = as.numeric(ifelse(host_acceptance_rate %in% c("N/A",""),NA,gsub("%","",host_acceptance_rate)))/100,
        host_experience = as.numeric(as.Date(calendar_last_scraped,format="%Y-%m-%d") -
                                as.Date(host_since ,format="%Y-%m-%d")),
         amenities = gsub('\\\"\"',"",amenities),
         amenities = gsub("\\\\u00e9","é",amenities),
         amenities = gsub("\\\\u00f6","ö",amenities),
         amenities = gsub("\\\\u00fc","ü",amenities),
         amenities = gsub("\\\\u00df","ß",amenities),
         amenities = gsub("\\\\u00a0"," ",amenities),
         amenities = gsub("\\\\u00e4","ä",amenities),
         amenities = gsub("\\\\u2019","'",amenities),
         amenities = gsub("\\\\u2013","-",amenities),
         amenities = gsub("\\\\","″",amenities),
         amenities = gsub("\\[","",amenities),
         amenities = gsub("\\]","",amenities),
        amenities = tolower(amenities),
         host_is_superhost = ifelse(host_is_superhost=="t",1,ifelse(host_is_superhost=="f",0,NA)),
         host_has_profile_pic = ifelse(host_has_profile_pic=="t",1,ifelse(host_has_profile_pic=="f",0,NA)),
         host_identity_verified = ifelse(host_identity_verified=="t",1,ifelse(host_identity_verified=="f",0,NA)),
         has_availability = ifelse(has_availability=="t",1,ifelse(has_availability=="f",0,NA)),
        instant_bookable = ifelse(instant_bookable=="t",1,ifelse(instant_bookable=="f",0,NA)),
        accommodates_sq=accommodates^2, 
        ln_accommodates=log(accommodates) ,
        ln_accommodates_sq=log(accommodates)^2,
        ln_beds = log(beds),
        ln_number_of_reviews = log(number_of_reviews+1)) %>% 
  select(-c(room_type,bathrooms_text))

#dig into amenities. After preprocessing, I try to group them as much as possible
listings_clean <- listings_clean %>% 
  mutate(da_coffe = ifelse(str_detect(amenities,"coffee"),1,0),
         da_tv = ifelse(str_detect(amenities,"hdtv |tv "),1,0),
         da_coalarm = ifelse(str_detect(amenities,"carbon monoxide"),1,0),
         da_smokealarm = ifelse(str_detect(amenities,"smoke"),1,0),
         da_kitchen = ifelse(str_detect(amenities,"kitchen"),1,0),
         da_wifi = ifelse(str_detect(amenities,"wifi"),1,0),
         da_fastwifi = ifelse(str_detect(amenities,"fast wifi"),1,0),
         da_workspace = ifelse(str_detect(amenities,"workspace"),1,0),
         da_parking = ifelse(str_detect(amenities,"parking|carport"),1,0),#paid or free?
         da_cleaningprod = ifelse(str_detect(amenities,"cleaning products"),1,0),
         da_micro = ifelse(str_detect(amenities,"microw|mikrow|micro and oven"),1,0),
         da_oven = ifelse(str_detect(amenities,"oven"),1,0),
         da_cloth_store = ifelse(str_detect(amenities,"clothing storage|dresser"),1,0),
         da_bikes = ifelse(str_detect(amenities,"bikes"),1,0),
         da_fridge = ifelse(str_detect(amenities,"fri"),1,0),
         da_dishwasher = ifelse(str_detect(amenities,"dishwasher"),1,0),
         da_washer = ifelse(str_detect(amenities,"washer")&amenities!="dishwasher",1,0),
         da_lt_stay = ifelse(str_detect(amenities,"long term"),1,0),
         da_packnplay = ifelse(str_detect(amenities,"pack"),1,0),
         da_withview = ifelse(str_detect(amenities,"view|waterfront"),1,0),
         da_heating = ifelse(str_detect(amenities,"heating|heated")&amenities!="pool - heated",1,0),
         da_bathroom_ess = ifelse(str_detect(amenities,"bathroom essentials|bath tub soaps|shower gel|shampoo|body soap|conditioner"),1,0),
         da_balcony = ifelse(str_detect(amenities,"balcony"),1,0),
         da_backyard = ifelse(str_detect(amenities,"backyard"),1,0),
         da_smoking = ifelse(str_detect(amenities,"smoking"),1,0),
         da_children_book = ifelse(str_detect(amenities,"children's book"),1,0),
         da_pets = ifelse(str_detect(amenities,"pets"),1,0),
         da_ac = ifelse(str_detect(amenities,"air conditioning"),1,0),
         da_hairdryer = ifelse(str_detect(amenities,"hair dryer"),1,0),#very highly correlated with dryer, latter not included
         da_soundsystem = ifelse(str_detect(amenities,"sound system"),1,0),
         da_highchair = ifelse(str_detect(amenities,"high chair"),1,0),
         da_fan = ifelse(str_detect(amenities,"fan"),1,0),
         da_breakfast = ifelse(str_detect(amenities,"breakfast"),1,0),
         da_iron = ifelse(str_detect(amenities,"iron"),1,0),
         da_hostgreet = ifelse(str_detect(amenities,"host"),1,0),
         #da_selfcheckin = ifelse(str_detect(amenities,"self"),1,0),very highly correlated with the above
         da_boardgame = ifelse(str_detect(amenities,"board"),1,0),
         da_freezer = ifelse(str_detect(amenities,"freezer"),1,0),
         da_elevator = ifelse(str_detect(amenities,"elevator"),1,0),
         da_firstaid = ifelse(str_detect(amenities,"first"),1,0),
         da_toaster = ifelse(str_detect(amenities,"toaster"),1,0),
         da_babyfriendly = ifelse(str_detect(amenities,"baby"),1,0),
         da_fireext = ifelse(str_detect(amenities,"extinguisher"),1,0),
         da_stove = ifelse(str_detect(amenities,"stove"),1,0),
         da_kettle = ifelse(str_detect(amenities,"kettle"),1,0),
         da_singlelevel = ifelse(str_detect(amenities,"single level"),1,0),
         da_luxury = ifelse(str_detect(amenities,"private pool|private sauna|private beach|private indoor pool|private outdoor pool|private hot tub"),1,0),
         da_gym = ifelse(str_detect(amenities,"gym"),1,0),
         da_host_org = ifelse(str_detect(tolower(host_name),"apart|home|blueground|residence|hotel|living|flat|rental|vienna|suit|flarent|team|immo|gmbh|feelgood"),1,0),
         f_host_response_time =factor(ifelse(host_response_time=="","N/A",host_response_time)),
         availability_year_share = availability_365/365) %>% 
  select(-c(host_id,host_since,host_name,host_location,name,description,neighborhood_overview,host_about,host_verifications,host_response_time,host_listings_count,neighbourhood,latitude,longitude,amenities,price,calendar_last_scraped,property_type,neighbourhood_cleansed,minimum_minimum_nights,minimum_maximum_nights,maximum_minimum_nights,maximum_maximum_nights,availability_30,availability_60,availability_90,availability_365,number_of_reviews_ltm,number_of_reviews_l30d,first_review,last_review,starts_with("review_score"),starts_with("calculated"),host_response_rate,host_acceptance_rate,bedrooms,minimum_nights_avg_ntm,maximum_nights_avg_ntm,reviews_per_month,))

listings_clean <- listings_clean %>% 
  mutate(f_minimum_nights= cut(minimum_nights, c(1,2,3,max(listings_clean$minimum_nights)), labels=c(1,2,3), right = F))

listings_clean <- listings_clean %>% 
  mutate(bathrooms =  ifelse(is.na(bathrooms), median(bathrooms, na.rm = T),bathrooms), #assume at least 1 bath
    beds = ifelse(is.na(beds), accommodates, beds), #assume n_beds=n_accomodates
    f_minimum_nights=ifelse(is.na(f_minimum_nights),1, f_minimum_nights),
    ln_beds=ifelse(is.na(ln_beds),0, ln_beds),
    host_experience = ifelse(is.na(host_experience), median(host_experience, na.rm = T),host_experience),
    host_total_listings_count = ifelse(is.na(host_total_listings_count), median(host_total_listings_count, na.rm = T),host_total_listings_count),
    host_has_profile_pic=ifelse(is.na(host_has_profile_pic),0, host_has_profile_pic),
    host_identity_verified=ifelse(is.na(host_identity_verified),0, host_identity_verified)) %>% 
  filter(price_usd <= 1000) %>% #99th percentile is 456, so it is not a binding threshold
  filter(host_total_listings_count<=1000) #also removing very a few data points

#Some character variables are not really meaningful or do not exhibit large variations
  #host location: mostly Vienna, empty, or (lower-) Austria
  #host verification: mostly email and/or phone
  #description/neighbourhood overview could be further extracted --> location, accessibility, floor, closeness of sights, amenities etc., but it is out of scope
  #and some are already used (to create a different feature), so they can be now dropped
  #review scores overall/in different areas: might be useful for a different model, but these are NEW listings, so reviews cannot help in the initial price setting (might help afterwards though). However, host attributes can matter as there is nothing about the host being new/existing with different listings

to_filter <- sapply(listings_clean, function(x) sum(is.na(x)))
to_filter[to_filter > 0]
```


# __Predicting Airbnb prices in small and medium-size apartments__

## Data collection

Data is from the <span style="text-decoration:underline">[Inside Airbnb site](http://insideairbnb.com/get-the-data.html)</span>, I selected the city of *Vienna* for the most recent time period available. The raw data consists of `r nrow(listings)` observations. After filtering for size (small and medium) and number of guests (2-6), and cleaning the data sufficiently, the sample size consists of `r nrow(listings_clean)` observations.

## Data exploration and dropping features

Several features of the data is not needed as

1. They are not conveying any information (large number of missing values which cannot be computed, very low variation, etc.)
2. They are not valid as this task is designed for new listings on the market
3. There are (or there can be created) other features that incorporate the characteristics of that feature as well

Based on these points, the following more important variables were dropped:

- review scores measures, listing's number of days on the market, host response rate, host acceptance rate, bedrooms
- some features needed imputed values - either with the median value, or if categorical, then by negative (false) value
- number of `NA`-s were very low in the remaining features --> required little imputation

Finally, the target variable (*price usd*) needed filtering as there were some massive outlier in the data. However, a threshold of 1000$ was sufficient, which resulted in the loss of less than 1% of the data.

```{r,echo=FALSE,warning=FALSE,fig.align='center',fig.height=3.75,fig.width=6}
ggplot(listings_clean,aes(x = f_neighbourhood_cleansed,y=price_usd))+
  geom_boxplot()+
  labs(x = "District", y="Price (USD)")+
  theme_bw()+
  theme(axis.title = element_text(size = 9),
        axis.text = element_text(size = 7,color="black"),
        axis.text.x = element_text(size = 7,color="black",angle=90))+
  scale_y_continuous(labels = scales::dollar_format())

```

Innere Stadt (first district) clearly stands out, it is much more expensive on average than any other districts in Vienna. Wieden (4th), Mariahilf (6th) and Neubau (7th) are also on top as they constitute the inner, historic part of the city, close to the canal and several sights.

```{r,echo=FALSE,fig.height=3.75,fig.width=6}

b1 <- ggplot(listings_clean,aes(x = host_total_listings_count, y = price_usd,color = as.factor(da_parking)))+
  geom_point()+
  labs(x = "Total listings of host",y="Price (USD)")+
  theme_bw()+
  theme(axis.title = element_text(size = 9),
        axis.text = element_text(size = 8,color="black"),
        legend.title = element_text(size = 8),
        legend.text = element_text(size = 7))+
  scale_y_continuous(labels = scales::dollar_format())+
  scale_color_manual(name="Parking availability",labels=c("0"="No","1"="Yes"),
                     values = c("red","steelblue"))
b2 <- ggplot(listings_clean,aes(x = bathrooms, y = price_usd,color = as.factor(da_ac)))+
  geom_point()+
  labs(x = "Number of bathrooms",y="Price (USD)")+
  theme_bw()+
  theme(axis.title = element_text(size = 9),
        axis.text = element_text(size = 8,color="black"),
        legend.title = element_text(size = 8),
        legend.text = element_text(size = 7))+
  scale_y_continuous(labels = scales::dollar_format())+
  scale_color_manual(name="Air-conditioning",labels=c("0"="No","1"="Yes"),
                     values = c("red","steelblue"))

b3 <- ggplot(listings_clean,aes(x = host_experience, y = price_usd,color = as.factor(da_smoking)))+
  geom_point()+
  labs(x = "Experience of hosts in days",y="Price (USD)")+
  theme_bw()+
  theme(axis.title = element_text(size = 9),
        axis.text = element_text(size = 8,color="black"),
        legend.title = element_text(size = 8),
        legend.text = element_text(size = 7))+
  scale_y_continuous(labels = scales::dollar_format())+
  scale_color_manual(name="Smoking",labels=c("0"="Not allowed","1"="Allowed"),
                     values = c("red","steelblue"))

b4 <- ggplot(listings_clean,aes(x = beds, y = price_usd,color = as.factor(instant_bookable)))+
  geom_point()+
  labs(x = "Number of beds",y="Price (USD)")+
  theme_bw()+
  theme(axis.title = element_text(size = 9),
        axis.text = element_text(size = 8,color="black"),
        legend.title = element_text(size = 8),
        legend.text = element_text(size = 7))+
  scale_y_continuous(labels = scales::dollar_format())+
  scale_color_manual(name="Instantly bookable",labels=c("0"="No","1"="Yes"),
                     values = c("red","steelblue"))
grid.arrange(b1,b2,b3,b4,nrow=2,ncol=2,
             bottom = textGrob("Observations above $1000 are removed.",hjust = 0,x=0.6,gp = gpar(fontsize = 7)))
```

## Models and methods used

The target variable is **nightly price** across all models.

1. Model 1: OLS model; $accommodates+beds+property\:type+bathrooms+neighbourhood + instant\:bookable + host\:attributes + accommodates^2+interactions$
2. Model 2: OLS model; $Model_1 + amenities$
3. Model 3: LASSO, based on $Model_2$
4. Model 4: Random Forest

The interactions include 

- $accommodates\times property\;type$, $air conditioning\times property\;type$, $pets\times property\;type$
- $accommodates\times neighbourhood$, $property\;type\times neighbourhood$

```{r,include=FALSE}
#LASSO

# Selecting features
basic_vars <- c(
  'accommodates', 'beds',
  'f_property_type','bathrooms',
  'f_neighbourhood_cleansed','instant_bookable')

# host attributes
host <- c("host_is_superhost","host_has_profile_pic",
          "host_total_listings_count","host_identity_verified","host_experience")

# Dummy variables
amenities <-  grep('^da_.*', names(listings_clean), value = TRUE)

#For LASSO
poly_lev <- c('accommodates_sq')

#interactions for the LASSO
X1  <- c('accommodates*f_property_type',
         'da_ac*f_property_type', 'da_pets*f_property_type')
# with districts
X2  <- c('f_property_type*f_neighbourhood_cleansed',
         'accommodates*f_neighbourhood_cleansed')

model_lasso1 <- paste0(' ~ ',paste(c(basic_vars,host),collapse = ' + '))
model_lasso2 <- paste0(' ~ ',paste(c(basic_vars,host,poly_lev),collapse = ' + '))
model_lasso3 <- paste0(' ~ ',paste(c(basic_vars,host,poly_lev,X1,X2),collapse = ' + '))
model_lasso4 <- paste0(' ~ ',paste(c(basic_vars,host,poly_lev,X1,X2,amenities),collapse = ' + '))

set.seed(0201)
train_indices <- as.integer(createDataPartition(listings_clean$price_usd, p = 0.75, list = FALSE))
data_train    <- listings_clean[train_indices, ]
data_holdout  <- listings_clean[-train_indices, ]
data_work <- data_train

k_folds <- 5
# Define seed value
seed_val <- 20230210

for (i in 1:4){
  print(paste0('Estimating model: ' ,i))
  model_name <-  paste0('model_lasso',i)
  model_pretty_name <- paste0('M',i,'')
  yvar <- 'price_usd'
  xvars <- eval(parse(text = model_name))
  formula <- formula(paste0(yvar,xvars))
  model_work_data <- feols(formula, data = data_work, vcov='hetero')
  
  fs  <- fitstat(model_work_data,c('rmse','r2','bic'))
  BIC <- fs$bic
  r2  <- fs$r2
  rmse_train <- fs$rmse
  ncoeff <- length(model_work_data$coefficients)
  set.seed(seed_val)
  cv_i <- train(formula, data_work, method = 'lm', 
                 trControl = trainControl(method = 'cv', number = k_folds))
  rmse_test <- mean(cv_i$resample$RMSE)
  model_add <- tibble(Model=model_pretty_name, Coefficients=ncoeff,
                      R_squared=r2, BIC = BIC, 
                      Training_RMSE = rmse_train, Test_RMSE = rmse_test)
  if (i == 1){
    model_results <- model_add
  } else{
    model_results <- rbind(model_results, model_add)
  }
}


# RMSE training vs test graph
colors = c('Training RMSE'='green','Test RMSE' = 'blue')
ggplot(data = model_results, aes(x = factor(Coefficients), group = 1))+
  geom_line(aes(y = Training_RMSE, color = 'Training RMSE'), size = 1) +
  geom_line(aes(y = Test_RMSE, color = 'Test RMSE'), size = 1)+
  labs(y='RMSE',x='Number of coefficients',color = '')+
  scale_color_manual(values = colors)+
  theme_bw()+
  theme(legend.position='top')

vars_model_4 <- c('price_usd',basic_vars,host,poly_lev,X1,X2,amenities)

train_control <- trainControl(method = 'cv', number = k_folds)
tune_grid     <- expand.grid('alpha' = c(1), 'lambda' = seq(0.05, 1, by = 0.05))
formula <- formula(paste0('price_usd ~ ', paste(setdiff(vars_model_4, 'price_usd'), collapse = ' + ')))

set.seed(seed_val)
lasso_model <- caret::train(formula,
                      data = data_work,
                      method = 'glmnet',
                      preProcess = c('center', 'scale'),
                      trControl = train_control,
                      tuneGrid = tune_grid,
                      na.action=na.exclude)
lasso_model$bestTune
lasso_model$bestTune$lambda
plot(lasso_model)

lasso_coeffs <- coef(lasso_model$finalModel, lasso_model$bestTune$lambda) %>%
  as.matrix() %>%
  as.data.frame() %>%
  rownames_to_column(var = 'variable') %>%
  rename(coefficient = `s1`)
#Features with shrunk coefficient
lasso_coeffs_nz<-lasso_coeffs %>%
  filter(coefficient!=0)

lasso_fitstats <- lasso_model$results %>%
  filter(lambda == lasso_model$bestTune$lambda) 
lasso_add <- tibble(Model='LASSO', Coefficients=nrow(lasso_coeffs_nz),
                    R_squared=lasso_fitstats$Rsquared, BIC = NA, 
                    Training_RMSE = NA, Test_RMSE = lasso_fitstats$RMSE)
# Add it to final results
model_results <- rbind(model_results, lasso_add)

#evaluate
m3 <- feols(formula(paste0('price_usd',model_lasso3)), data = data_work, vcov = 'hetero')
m4 <- feols(formula(paste0('price_usd',model_lasso4)), data = data_work, vcov = 'hetero')

# Make prediction for the hold-out sample with each models
m3_p <- predict(m3, newdata = data_holdout)
m4_p <- predict(m4, newdata = data_holdout)
mL_p <- predict(lasso_model, newdata = data_holdout)

# Calculate the RMSE on hold-out sample
m3_rmse <- RMSE(m3_p,data_holdout$price_usd)
m4_rmse <- RMSE(m4_p,data_holdout$price_usd)
mL_rmse <- RMSE(mL_p,data_holdout$price_usd)
# Create a table
sum <- rbind(m3_rmse,m4_rmse,mL_rmse)
rownames(sum) <- c('Model 3','Model 4','LASSO')
colnames(sum) <- c('RMSE on hold-out sample')
sum
```

```{r,include=FALSE}
predictors_1 <- c(basic_vars)
predictors_2 <- c(basic_vars, host, amenities)
predictors_E <- c(basic_vars, host, amenities, X1,X2)

# do 5-fold CV
train_control <- trainControl(method = 'cv',
                              number = 5,
                              verboseIter = FALSE)
tune_grid <- expand.grid(
  .mtry = c(8),
  .splitrule = 'variance',
  .min.node.size = c(50)
)

set.seed(12345)
system.time({
rf_model_1 <- train(
  formula(paste0('price_usd ~', paste0(predictors_1, collapse = ' + '))),
  data = data_train,
  method = 'ranger',
  trControl = train_control,
  tuneGrid = tune_grid,
  importance = 'impurity'
)
})

set.seed(12345)
system.time({
rf_model_2 <- train(
  formula(paste0('price_usd ~', paste0(predictors_2, collapse = ' + '))),
  data = data_train,
  method = 'ranger',
  trControl = train_control,
  tuneGrid = tune_grid,
  importance = 'impurity'
)
})

results <- resamples(
  list(
    model_1  = rf_model_1,
    model_2  = rf_model_2
 )
)
```


```{r,echo=FALSE,fig.height=3.75,fig.width=6}
rf_model_2_var_imp <- ranger::importance(rf_model_2$finalModel)/1000
rf_model_2_var_imp_df <-
  data.frame(varname = names(rf_model_2_var_imp),imp = rf_model_2_var_imp) %>%
  mutate(varname = gsub('f_neighbourhood_cleansed', 'District: ', varname)) %>%
  mutate(varname = gsub('f_property_type', 'Property type:\n', varname)) %>%
  arrange(desc(imp)) %>%
  mutate(imp_percentage = imp/sum(imp))

cutoff = 500
ggplot(rf_model_2_var_imp_df[rf_model_2_var_imp_df$imp>cutoff,],
                                  aes(x=reorder(varname, imp), y=imp_percentage)) +
  geom_point(color='red', size=1.5) +
  geom_segment(aes(x=varname,xend=varname,y=0,yend=imp_percentage), color='red',size=1)+
  labs(title="Variable importance plot",y = 'Importance (Percent)', x= 'Variable name',caption = "Importance threshold above 500.") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_bw() +
  theme(axis.text = element_text(size=7,color="black"),
        axis.title = element_text(size=8,color = "black"),
        plot.title = element_text(size =10,hjust =0.5),
        plot.caption = element_text(size = 7))
```

```{r,echo=FALSE,fig.height=3.75,fig.width=6}
ggplot(rf_model_2_var_imp_df[1:10,], aes(x=reorder(varname, imp), y=imp_percentage)) +
  geom_point(color='red', size=1) +
  geom_segment(aes(x=varname,xend=varname,y=0,yend=imp_percentage), color='red', size=0.75) +
  labs(title="Variable importance plot",y = 'Importance (Percent)', x= 'Variable name',caption = "Top 10 features.") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_bw()+
  theme(axis.text = element_text(size=7,color="black"),
        axis.title = element_text(size=8,color = "black"),
        plot.title = element_text(size =10,hjust =0.5),
        plot.caption = element_text(size = 7))
```

